---
title: "IFdosingStats - 20 trial blocks"
output: html_document
usage: You must make sure the Rdata files from "interferenceDosing_stats.R" have been sucessfully run, and that the stats files are in the "R output files" folder on the drive. Make sure you have set blocksize = 20
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(ez)
setwd("/Volumes/mnl/Data/Adaptation/interference_dosing/R output files/20 trial blocks")
load(file = "lhKinematics_stats.Rdata") # Currently blocked by 20 trials
load(file = "rhKinematics_stats.Rdata")
```

# Baseline Phases - NON-standardized
## Left hand
### IDE_c VB
```{r, echo=FALSE}
# IDE - Visual Baseline
ezANOVA(subset(lhKinematics_stats, block %in% c(1)), dv = ide_c, between = group, wid = subjectID)
```

### EP_X_c VB
```{r, echo=FALSE}
# EPX - Visual Baseline
ezANOVA(subset(lhKinematics_stats, block %in% c(1)), dv = EP_X_c, between = group, wid = subjectID)
```

### IDE_c KB
```{r, echo=FALSE}
# IDE - Kin Baseline
ezANOVA(subset(lhKinematics_stats, block %in% c(2)), dv = ide_c, between = group, wid = subjectID)
```

### EP_X_c KB
```{r, echo=FALSE}
# EPX - Kin Baseline
ezANOVA(subset(lhKinematics_stats, block %in% c(2)), dv = EP_X_c, between = group, wid = subjectID)
```

## Right Hand
### IDE_c VB
```{r, echo=FALSE}
# IDE - Visual Baseline
ezANOVA(subset(rhKinematics_stats, block %in% c(1)), dv = ide_c, between = group, wid = subjectID)
```

### EP_X_c VB
```{r, echo=FALSE}
# EPX - Visual Baseline
ezANOVA(subset(rhKinematics_stats, block %in% c(1)), dv = EP_X_c, between = group, wid = subjectID)
```

### IDE_c KB
```{r, echo=FALSE}
# IDE - Kin Baseline
ezANOVA(subset(rhKinematics_stats, block %in% c(2)), dv = ide_c, between = group, wid = subjectID)
```

### EP_X_c KB
```{r, echo=FALSE}
# EPX - Kin Baseline
ezANOVA(subset(rhKinematics_stats, block %in% c(2)), dv = EP_X_c, between = group, wid = subjectID)
```

# Exposure Phases - Middle and End
## Left hand
### IDE_c EX
```{r, echo=FALSE}
# IDE - Exposure
ezANOVA(subset(lhKinematics_stats, block %in% c(6,9)), dv = ide_c, within = block, between = group, wid = subjectID)
```

### EP_X_c EX
```{r, echo=FALSE}
# EPX - Exposure
ezANOVA(subset(lhKinematics_stats, block %in% c(6,9)), dv = EP_X_c, within = block, between = group, wid = subjectID)
```


## Right Hand
### IDE_c EX
```{r, echo=FALSE}
# IDE - Exposure
ezANOVA(subset(rhKinematics_stats, block %in% c(6,9)), dv = ide_c, within = block, between = group, wid = subjectID)
```

### EP_X_c EX
```{r, echo=FALSE}
# EPX - Exposure
ezANOVA(subset(rhKinematics_stats, block %in% c(6,9)), dv = EP_X_c, within = block, between = group, wid = subjectID)
```

# Post-Exposure Phases
## Left hand
### IDE_c PE
```{r, echo=FALSE}
# IDE - Post-Exposure
ezANOVA(subset(lhKinematics_stats, block %in% c(10,11)), dv = ide_c, within = block, between = group, wid = subjectID)
```

### EP_X_c PE
```{r, echo=FALSE}
# EPX - Post-Exposure
ezANOVA(subset(lhKinematics_stats, block %in% c(10,11)), dv = EP_X_c, within = block, between = group, wid = subjectID)
```


## Right Hand
### IDE_c PE
```{r, echo=FALSE}
# IDE - Post-Exposure
ezANOVA(subset(rhKinematics_stats, block %in% c(10,11)), dv = ide_c, within = block, between = group, wid = subjectID)
```

### EP_X_c PE
```{r, echo=FALSE}
# EPX - Post-Exposure
ezANOVA(subset(rhKinematics_stats, block %in% c(10,11)), dv = EP_X_c, within = block, between = group, wid = subjectID)
```

# LFoff_FS Data
## Vis Baseline
```{r, echo=FALSE}
ezANOVA(subset(lhKinematics_stats, block %in% c(1)), dv = LFoff_FS_c,  between = group, wid = subjectID)
```

## Kin Baseline
```{r, echo=FALSE}
ezANOVA(subset(lhKinematics_stats, block %in% c(2)), dv = LFoff_FS_c, between = group, wid = subjectID)
```

## Exposure Middle-End
```{r, echo=FALSE}
ezANOVA(subset(lhKinematics_stats, block %in% c(6,9)), dv = LFoff_FS_c, within = block, between = group, wid = subjectID)
```

## Post-Exposure
```{r, echo=FALSE}
ezANOVA(subset(lhKinematics_stats, block %in% c(10,11)), dv = LFoff_FS_c, within = block, between = group, wid = subjectID)
```

# LFoff.bc Data
## Vis Baseline
```{r, echo=FALSE}
ezANOVA(subset(lhKinematics_stats, block %in% c(1)), dv = LFoff.bc,  between = group, wid = subjectID)
```

## Kin Baseline
```{r, echo=FALSE}
#ezANOVA(subset(lhKinematics_stats, block %in% c(2)), dv = LFoff.bc, between = group, wid = subjectID) # Need to comment this out because residual sum of squares is zero (ie: no sig diff)
```

## Exposure Middle-End
```{r, echo=FALSE}
ezANOVA(subset(lhKinematics_stats, block %in% c(6,9)), dv = LFoff.bc, within = block, between = group, wid = subjectID)
```

## Post-Exposure
```{r, echo=FALSE}
ezANOVA(subset(lhKinematics_stats, block %in% c(10,11)), dv = LFoff.bc, within = block, between = group, wid = subjectID)
```